\textit{Supplementary materials for: } High-level cognition during story listening is reflected in high-order dynamic correlations in neural activity patterns

### 2019-09-06 paper/supporting_information.tex
updated supplemental materials caption

@@

\begin{figure}[tp]
\centering
\includegraphics[width=1\textwidth]{figs/stats_heatmaps}
\caption{\textbf{Statistical summary of decoding accuracies for
    different neural features.}  Each heatmap displays decoding
  results for one experimental condition (intact, paragraph, word, and
  rest).  We considered dynamic activity patterns (order 0) and
  dynamic correlations at different orders (order $> 0$).  We used
  two-tailed $t$-tests to compare the
  distributions of decoding accuracies obtained using each pair of
  features.  The distributions for each feature reflect the set of
  average decoding accuracies (across all kernel parameters), obtained
  for each random assignment of training and test groups.
  In the upper triangles of each map, warmer colors (positive $t$-values) indicate that the
  neural feature indicated in the given row yielded higher accuracy than the
  feature indicated in the given column.  Cooler colors (negative
  $t$-values) indicate that
  the feature in the given row yielded lower decoding accuracy than
  the feature in the given column.  The lower triangles of each map
  denote the corresponding $p$-values for the $t$-tests.  The diagonal
  entries display the relative average optimized weight given to each type of feature, in
  a decoder that included all feature types (see \textbf{Feature
    weighting and testing}).}
\label{fig:stats_heatmaps}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=0.75\textwidth]{figs/supp_15_intact}
\caption{\textbf{Top 10 terms associated with the endpoints of the
      strongest correlations for the intact experimental condition.}  Each color corresponds to orders 1-15 of
    inter-subject functional correlations. The inflated brain plots
    display the locations of the endpoints of the 10 strongest
    (absolute value) correlations at each order, projected onto the
    cortical surface~\citep{CombEtal19}.  The lists of terms on the
    right display the top 10 Neurosynth terms~\citep{RubiEtal17}
    decoded from the corresponding brain maps for each order for the intact condition.}
\label{fig:intact}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=0.75\textwidth]{figs/supp_15_paragraph}
\caption{\textbf{Top 10 terms associated with the endpoints of the
      strongest correlations for the paragraph scrambled condition.}  Each color corresponds to orders 1-15 of
    inter-subject functional correlations for the paragraph scrambled condition. The inflated brain plots
    display the locations of the endpoints of the 10 strongest
    (absolute value) correlations at each order, projected onto the
    cortical surface~\citep{CombEtal19}.  The lists of terms on the
    right display the top 10 Neurosynth terms~\citep{RubiEtal17}
    decoded from the corresponding brain maps for each order.}
\label{fig:paragraph}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=0.75\textwidth]{figs/supp_15_word}
\caption{\textbf{Top 10 terms associated with the endpoints of the
      strongest correlations for the word scrambled condition.}  Each color corresponds to orders 1-15 of
    inter-subject functional correlations for the word scrambled condition. The inflated brain plots
    display the locations of the endpoints of the 10 strongest
    (absolute value) correlations at each order, projected onto the
    cortical surface~\citep{CombEtal19}.  The lists of terms on the
    right display the top 10 Neurosynth terms~\citep{RubiEtal17}
    decoded from the corresponding brain maps for each order.}
\label{fig:word}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=0.75\textwidth]{figs/supp_15_rest}
\caption{\textbf{Top 10 terms associated with the endpoints of the
      strongest correlations for the rest condition.}  Each color corresponds to orders 1-15 of
    inter-subject functional correlations for the rest condition. The inflated brain plots
    display the locations of the endpoints of the 10 strongest
    (absolute value) correlations at each order, projected onto the
    cortical surface~\citep{CombEtal19}.  The lists of terms on the
    right display the top 10 Neurosynth terms~\citep{RubiEtal17}
    decoded from the corresponding brain maps for each order.}
\label{fig:rest}
\end{figure}

>>>>

\newcommand{\neurosynth}{7}

@@

\begin{figure}[p!]
\centering
\includegraphics[width=0.75\textwidth]{figs/supp_15_intact}
\caption{\textbf{Top terms associated with the endpoints of the
    strongest correlations for the \textit{intact} experimental
    condition.}  Each color corresponds to one order of inter-subject
functional correlations. The inflated brain plots display the
locations of the endpoints of the 10 strongest (absolute value)
correlations at each order, projected onto the cortical
surface~\citep{CombEtal19}.  The lists of terms display
the top 10 Neurosynth terms~\citep{RubiEtal17} decoded from the
corresponding brain maps for each order.  (Also see Fig.~\neurosynth,
top row, in the main text.)}
\label{fig:intact}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=0.75\textwidth]{figs/supp_15_paragraph}
\caption{\textbf{Top terms associated with the endpoints of the
    strongest correlations for the \textit{paragraph} experimental
    condition.}  This figure is in the same format as
  Figure~\ref{fig:intact}, but displays results for the
  paragraph-scrambled story listening condition.  (Also see Fig.~\neurosynth,
second row, in the main text.)}
\label{fig:paragraph}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=0.75\textwidth]{figs/supp_15_word}
\caption{\textbf{Top terms associated with the endpoints of the
    strongest correlations for the \textit{word} experimental
    condition.}  This figure is in the same format as
  Figure~\ref{fig:intact}, but displays results for the
  word-scrambled story listening condition.  (Also see Fig.~\neurosynth,
third row, in the main text.)}
\label{fig:word}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=0.75\textwidth]{figs/supp_15_rest}
\caption{\textbf{Top terms associated with the endpoints of the
    strongest correlations for the \textit{rest} experimental
    condition.}  This figure is in the same format as
  Figure~\ref{fig:intact}, but displays results for the
  resting state condition.  (Also see Fig.~\neurosynth,
bottom row, in the main text.)}
\label{fig:rest}
\end{figure}
